Reasoning Graphically about Quantum Computation

### 2008-03-03 papers/reasoning-graphically/paper.tex
more small changes
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1397 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

\begin{theorem}
  $G \leq_v H \Leftrightarrow \vinterp{G} \supseteq \vinterp{H}$. 
\end{theorem}

@@

\begin{definition}
  Two mappings $f_G$ and $f_H$ \emph{agree} when $\forall v \in
  f_G(G).\, f_H(v) \in f^{-1}_G(v)$ and $\forall v \in f_H(H).\,
  f_G(v) \in f^{-1}_H(v)$. This states when a set of nodes in one
  graph all map to a common node $n$ in the other graph, $n$ maps back
  to one of the nodes that maps to it. 
\end{definition}

We let $\pi(G,H)$ abbreviate $\exists p.\,\pi_p(G,H)$. We also
overload the notation $\pi_p(G,H)$ to let it denote the graph that
results from the plugging. This is defined to be the union of the
nodes and edges from $G$ and $H$ where the nodes and edges mapped by
the pair of plugging function are identified. Identification of nodes
instantiates variable nodes: when a variable node is mapped to a
concrete one, the result is a concrete node.

@@

\begin{theorem}
  \emph{Match after plugging}: $G \leq \pi_f(G,H)$. And as a corrolary
  we get $H \leq \pi_f(G,H)$ by symmetry of plugging. 
\end{theorem}

\begin{theorem}
  \emph{Plugging preserves matching}: $V \leq G \Rightarrow V \leq
  \pi_f(G,H)$. As corrolaries we get $V \leq H \Rightarrow V \leq
  \pi_f(G,H)$ from symmetry of plugging and $\vinterp{G} \cap
  \vinterp{H} \subseteq \bigcup_f \vinterp{\pi_f(G,H)}$ from the
  definition of interpretation. 
\end{theorem}

>>>>

\begin{theorem}
\label{match-interp-thm}
  $G \leq_v H \Leftrightarrow \vinterp{G} \supseteq \vinterp{H}$. Proof... 
\end{theorem}

\begin{theorem}
\label{reflexive-match-thm}
  \emph{Matching is reflexive}: $G \leq_v G$ is a trivial consequence from open-embedding. 
\end{theorem}

@@

\begin{definition}
  Two mappings $f_G$ and $f_H$ \emph{agree} when $\forall v \in
  f_G(G).\, f_H(v) \in f^{-1}_G(v)$ and $\forall v \in f_H(H).\,
  f_G(v) \in f^{-1}_H(v)$. This states that if a set of nodes in one
  graph all map to a common node, $n$, in the other graph, then $n$
  maps back to one of the nodes that maps to it.
\end{definition}

We let $\pi(G,H)$ abbreviate $\exists p.\,\pi_p(G,H)$. We also
overload the notation $\pi_p(G,H)$ to let it denote the graph that
results from the plugging. This is defined to be the union of the
nodes and edges from $G$ and $H$ where the nodes and edges mapped by
the pair of plugging function are identified. Identification of nodes
instantiates variable nodes: when a variable node is mapped to a
concrete one, identification results in the concrete node.

@@

\begin{theorem}
  \emph{Plugging preserves matching}: $V \leq_v G \Rightarrow V \leq_v
  \pi_f(G,H)$. As corrolaries we get $V \leq_v H \Rightarrow V \leq_v
  \pi_f(G,H)$ from symmetry of plugging, $\vinterp{G} \cap \vinterp{H}
  \subseteq \bigcup_f \vinterp{\pi_f(G,H)}$ from the definition of
  interpretation, $G \leq_v \pi_f(G,H)$ from reflexivity of matching
  and consequently $H \leq_v \pi_f(G,H)$ by symmetry of plugging.
\end{theorem}
